\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{University of Queensland} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge Epistasis follow-up \\[0.3cm] \huge *** summary *** \\ \horrule{2pt} \\[0.5cm] \date{}

### 2015-04-30 investigation/docs/overview.tex
col figures added and code edited to make them

\begin{figure}[H]
\centering
\includegraphics[height=3in]{perm_vs_lambdaF.png}
\caption*{Figure | the relationship between the observed p values corrected for lambdaF, which was calculated from the GWAS-based analysis and the permutation empitical p-values}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[height=3in]{perm_vs_lambdaC.png}
\caption*{Figure | the relationship between the observed p values corrected for lambdaChisq, which was calculated from the GWAS-based analysis and the permutation empitical p-values}
\end{figure}

>>>>

\begin{figure}[H]
\centering
\includegraphics[height=3in]{perm_vs_lambdaF.png}
\caption*{Figure | the relationship between the observed p values corrected for lambdaF, which was calculated from the GWAS-based analysis and the permutation empitical p-values. Red are \emph{cis-cis}}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[height=3in]{perm_vs_lambdaC.png}
\caption*{Figure | the relationship between the observed p values corrected for lambdaChisq, which was calculated from the GWAS-based analysis and the permutation empitical p-values. Red are \emph{cis-cis}}
\end{figure}
